---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mrap

<!-- badges: start -->
<!-- badges: end -->

The goal of mrap is to provide wrapper functions to reduce the user's effort in writing machine-reusable data.    

## Installation

You can install the development version of mrap from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("OlgaLezhnina/mrap_R")
```

## Example

For instance, you have results of ANOVA on Iris data. On the help page, you see that the group_comparison schema should be used. Instead of writing the data manually with dtreg, use the group_comparison function from mrap.

```{r example}
library(mrap)
## get the data
attach(iris)
virginica <- iris[iris$Species== "virginica", ]
versicolor <- iris[iris$Species== "versicolor", ]
## run the test
my_anova <- stats::aov(Petal.Length ~ Species, iris)
## write the results as a data frame
my_results <- summary(my_anova)[[1]]
## use the relevant wrapper to write an instance
my_instance <-
  mrap::group_comparison("stats::aov(Petal.Length ~ Species, data = iris)",
                         iris,
                         my_results)
## make any changes to the instance
my_instance$label <- "ANOVA for Iris petal length"
## write the result as JSON-LD using dtreg
my_json <- dtreg::to_jsonld(my_instance)
```
Such wrappers as group_comparison have three arguments: code_string, input_data, and test_results. 

* Argument code_string should be a string (in R, a character vector) and include package::function notation. It usually starts the string 'package::function(formula)', but we also allow for generic method summary, then it can be 'summary(package::function(formula))'. 

* In code_string, the data label should be specified as "data = iris", not just "iris". Not specifying the data label is acceptable, please add it manually to the instance. 

* In code_string, target variable is recognized by our wrappers before the ~ sign in the formula (strings a, b, and c) or when explicitly specified in two or more vectors (string d). Otherwise, you will get a warning reminding to add the target label manually to the instance (strings e and f). 

```{r}
## (a) "package::function(Petal.Length ~ Species), data = iris"
## (b) "package::function(iris$Petal.Length ~ iris$Species), data = iris"
## (c) "package::function(cbind(Petal.Length, Petal.Width) ~ Species), data = iris"
## (d) "package::function(setosa$Petal.Length, virginica$Petal.Length)"
## (e) "package::function(one_vector, another_vector)"
## (f) "package::function(data_1$one_vector, data_2$another_vector)"
```
* In code_string, level variable is recognized by our wrappers in x|level notation. TODO.

* Argument input_data should be either a data frame or a named list. 

```{r}
# if you have a data frame, check it
is.data.frame(iris)
# for a few vectors or data frames, create a named list
species_list <- list("virginica" = virginica, "versicolor" = versicolor)
# check it is a list
is.list(species_list)
# check the names
names(species_list)
```


