---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mrap

<!-- badges: start -->
<!-- badges: end -->

The goal of mrap is to provide wrapper functions to reduce the user's effort in writing machine-reusable data.    

## Installation

You can install the development version of mrap from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("OlgaLezhnina/mrap_R")
```

## Example

For instance, you have results of ANOVA on Iris data. On the help page, you see that the group_comparison schema should be used. Instead of writing the data manually with dtreg, use the group_comparison function from mrap.

```{r example}
library(mrap)
## get the data
attach(iris)
## run the test
my_anova <- stats::aov(Petal.Length ~ Species, iris)
## write the results as a data frame
my_results <- summary(my_anova)[[1]]
## use the relevant wrapper to write an instance
my_instance <-
  mrap::group_comparison("stats::aov(Petal.Length ~ Species, data = iris)",
                         iris,
                         my_results)
## make any changes to the instance
my_instance$label <- "ANOVA for Iris petal length"
## write the result as JSON-LD using dtreg
my_json <- dtreg::to_jsonld(my_instance)
```
Such wrappers as group_comparison have three arguments: code_string, input_data, and test_results. 
* Argument code_string should be a string(in R, a character vector) and include package::function notation. 
* In code_string, the data label should be specified as "data = iris", not just "iris". Not specifying the data label is acceptable, please add it manually to the instance. 
* In code_string, target variable is recognized by our wrappers before the ~ sign in the formula (strings a, b, and c) or when explicitly specified in two or more vectors (string d). Otherwise (strings e or f) you will get a warning reminding to add the target name manually. 

```{r}
## (a) target variable
"package::function(Petal.Length ~ Species), data = iris"
## (b) data$target_variable
"package::function(iris$Petal.Length ~ iris$Species), data = iris"
## (c) a few target variables with cbind for MANOVA
"package::function(cbind(Petal.Length, Petal.Width) ~ Species), data = iris"

```
