---
title: "Introduction to mrap"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to mrap}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)
```

```{r setup}
library(mrap)
```

The goal of mrap is to provide wrapper functions to reduce the user's effort 
in writing machine-readable data with the [dtreg package](https://cran.r-project.org/package=dtreg).
The growing set of wrappers covers functions from  ``stats`` and other widely used packages.
Mrap also contains wrappers for analytical schemata 
used in the [ORKG-reborn approach](https://reborn.orkg.org/pages/help).

To write the results of your data analysis as JSON-LD:

* Select a wrapper for the schema you will use.

* Check the types of arguments the wrapper requires.

* Create an instance of the schema-related class.

* Modify the instance by setting or correcting its fields manually.

* Write the finalised instance as a machine-readable JSON-LD file with dtreg. 

## 1. Select a wrapper

## 2. Check arguments

#### 2.1. Code string
Argument ``code_string`` should be a string (in R, a character vector). The argument cannot be omitted; please indicate  ``'N/A'`` if this information is not provided.   

##### Package name
To specify the name of the package in the code is always a good practice. In mrap, we made it a requirement, and you will get an error message if the ``code_string`` does not contain  ``package::function``. In most cases, it is the beginning of the string, but we allow for generic method summary, in this case it is ``summary(package::function(formula))``. For base R, please indicate ``base::``.  

##### Data name
If you want mrap to extract the data name from the ``code_string``, please indicate it as ``'data = dataset_name'``, although many R packages also allow for merely ``dataset_name``. If the data name is not detected, it can be added manually to the instance (see Modify the instance). 

##### Target variable(s)
Our wrappers extract the name of a target variable from the ``code_string`` if the variable is before the ``~`` sign in the formula:

```{r}
"package::function(Petal.Length ~ Species), data = iris"
"package::function(iris$Petal.Length ~ iris$Species), data = iris"
```
We also allow for a few target variables in special cases such as MANOVA:

```{r}
"package::function(cbind(Petal.Length, Petal.Width) ~ Species), data = iris"
```
 
Alternatively, a target variable can be explicitly specified in two or more vectors:  

```{r}
"package::function(setosa$Petal.Length, virginica$Petal.Length)"
```
In the following case we cannot extract the name, and you can add the target label manually to the instance: 

```{r}
"package::function(one_vector, another_vector)"
```
You will get a warning reminding to do it. 

##### Level variable(s)
In ``code_string``, level variable is recognized by our wrappers in x|level notation. TODO.

#### 2.2. Input data

Argument ``input_data`` can be:

* a string, which is either a file name or a URL

```{r}
is.character("ABC")
```

* a dataframe

```{r}
is.data.frame(iris)
```
* a named list for a few vectors or data frames:

```{r}
species_list <- list("virginica" = virginica, "versicolor" = versicolor)
# check it is a list
is.list(species_list)
# check that the list is named
names(species_list)
```
Please be sure that the argument is one of these three types. You will get an error message if a type is wrong (for instance, a list instead of a named list).

#### 2.3. Test results or named list results

Argument ``test_results`` can be either a data frame or a list of data frames.
You can check whether you are writing down the argument correctly. For a data frame:

```{r}
is.data.frame(iris)
```
 For a list of data frames:

```{r}
# assume you have a few data frames in a list
iris_new <- iris[, -1]
my_results <- list(iris, iris_new)
# check each of them in a loop
for (element in my_results) {
  print(is.data.frame(element))
}
``` 
Argument ``named_list_results`` is only used for the ``algorithm_evaluation`` schema.
