---
title: "Introduction to mrap"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to mrap}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)
```

```{r setup}
library(mrap)
```

The goal of mrap is to provide wrapper functions to reduce the user's effort 
in writing machine-readable data with the [dtreg package](https://cran.r-project.org/package=dtreg).
The growing set of wrappers covers functions from stats and other widely used packages.
Mrap also contains wrappers for analytical schemata 
used in the [ORKG-reborn approach](https://reborn.orkg.org/pages/help).

To write the results of your data analysis as JSON-LD:

* Select a wrapper from mrap, check the types of arguments it requires, and create an instance.

* Modify the instance by setting or correcting its fields manually.

* Write the finalised instance as a machine-readable JSON-LD file with dtreg. 

## 1. Select a wrapper and create an instance


```{r}
dt <- dtreg::load_datatype("https://doi.org/21.T11969/b9335ce2c99ed87735a6")
```

### Check types of arguments

* Argument ``code_string`` should be a string (in R, a character vector) and include package::function notation. It usually starts the string 'package::function(formula)', but we also allow for generic method summary, then it can be 'summary(package::function(formula))'. 

* In ``code_string``, the data label should be specified as "data = iris", not just "iris". Not specifying the data label is acceptable, please add it manually to the instance. 

* In ``code_string``, target variable is recognized by our wrappers before the ~ sign in the formula (strings a, b, and c) or when explicitly specified in two or more vectors (string d). Otherwise, you will get a warning reminding to add the target label manually to the instance (strings e and f). 

```{r}
# (a) "package::function(Petal.Length ~ Species), data = iris"
# (b) "package::function(iris$Petal.Length ~ iris$Species), data = iris"
# (c) "package::function(cbind(Petal.Length, Petal.Width) ~ Species), data = iris"
# (d) "package::function(setosa$Petal.Length, virginica$Petal.Length)"
# (e) "package::function(one_vector, another_vector)"
# (f) "package::function(data_1$one_vector, data_2$another_vector)"
```
* In ``code_string``, level variable is recognized by our wrappers in x|level notation. TODO.

* Argument ``input_data`` should be either a data frame or a named list. 

```{r}
# if you have a data frame, check it
is.data.frame(iris)
# for a few vectors or data frames, create a named list
species_list <- list("virginica" = virginica, "versicolor" = versicolor)
# check it is a list
is.list(species_list)
# check the names
names(species_list)
```

